Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-15 ms.tex
Minor changes to wording in sections 1 and 2.

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We constrain the newly-introduced Decorated HOD model using SDSS DR7
  measurements of projected galaxy clustering, $\wprp,$ and number
  density, $n_{\rm g},$ made from r-band luminosity-threshold
  samples. The Decorated HOD is a model for the galaxy--halo
  connection that augments the traditional Halo Occupation
  Distribution (HOD) by allowing for the possibility of {\em assembly
    bias}: galaxy luminosity may be correlated with dark matter halo
  properties besides virial mass $\mvir$ alone. We demonstrate that it
  is not possible to rule out assembly bias using DR7 measurements of
  $\wprp$ and $n_{\rm g}.$ Moreover, galaxy samples $\magr<-20, -20.5$
  favor strong levels of central galaxy assembly bias:
  high-concentration halos are more likely to host a central galaxy
  relative to low-concentration halos of the same $\mvir.$ We rule out
  zero assembly bias with high significance for these
  samples. Satellite assembly bias only becomes significant for the
  faintest sample we study, $\magr<-19.$ We find no evidence for
  assembly bias in the $\magr<-21$ sample. Because the Decorated HOD
  subsumes the traditional HOD, and additionally because of errors
  made in the original analysis of these samples, our results differ
  from and supersede existing HOD constraints from low-redshift
  clustering measurements.
\end{abstract}

@@

This work presents a re-analysis of the SDSS DR7 data that 
overcomes numerous shortcomings of previous analyses. 
Our analysis improvements stem primarily from our 
directly populating mock galaxy catalogs into a cosmological simulation, 
whereas previous analyses relied upon analytical fitting functions 
with parameters calibrated against a suite of simulations. 
In direct mock population, delicate issues present in analytic
modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.  
Our approach also provides a natural framework for studying models of assembly bias, 
since we can use the exact clustering properties of simulated halos as a function of 
any arbitrary halo properties in the catalog. With direct mock population, 
systematic uncertainty in the model is limited to 
the sample variance of the simulated box, 
errors related to insufficient numerical resolution, 
and numerical inaccuracies of halo-finding (e.g., over-merging).

@@

The most important detail of this analysis is the priors on the parameters. In all analyses 
discussed in this paper, we adopt priors that are uniform distributions over the intervals 
specified in Table~\ref{table:priors}. In the case of the assembly bias parameters 
$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors represent physical 
boundaries. These parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
Physical considerations require parameter $\sigma_{\log M} > 0$. All other 
priors have a negligible influence on the posterior aside from $\log M_0$. 
We find that $\log M_0$ is often very poorly constrained by clustering data and 
priors on $\log M_0$ can have a non-negligible influence on inferred parameters.

>>>>

\maketitle
%----------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%  A B S T R A C T %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
  We constrain the newly-introduced Decorated HOD model using SDSS DR7
  measurements of projected galaxy clustering, $\wprp,$ and number
  density, $n_{\rm g},$ made from r-band luminosity-threshold
  samples. The Decorated HOD is a model for the galaxy--halo
  connection that augments the traditional Halo Occupation
  Distribution (HOD) by allowing for the possibility of {\em assembly
    bias}: galaxy luminosity may be correlated with dark matter halo
  properties besides virial mass $\mvir$ alone. We demonstrate that it
  is not possible to rule out assembly bias using DR7 measurements of
  $\wprp$ and $n_{\rm g}.$ Moreover, galaxy samples $\magr<-20, -20.5$
  favor strong levels of central galaxy assembly bias:
  high-concentration halos are more likely to host a central galaxy
  relative to low-concentration halos of the same $\mvir.$ We rule out
  zero assembly bias with high significance for these
  samples. Satellite assembly bias only becomes significant for the
  faintest sample we study, $\magr<-19.$ We find no evidence for
  assembly bias in the $\magr<-21$ sample. Because the Decorated HOD
  subsumes the traditional HOD, and additionally because the original 
  \citet{zehavi_etal11} analysis did not sufficiently sample the posterior distributions, 
 our results differ from and supersede existing HOD constraints from low-redshift
  clustering measurements.
\end{abstract}

@@

This work presents a re-analysis of the SDSS DR7 data that 
overcomes numerous shortcomings of previous studies. 
The main improvements accomplished by our approach stem primarily from our 
directly populating mock galaxy catalogs into a cosmological simulation, 
whereas previous analyses relied upon analytical fitting functions 
with parameters calibrated against a suite of simulations. 
In direct mock population, delicate issues present in analytic
modeling, such as scale-dependent halo bias and halo exclusion, are treated exactly.  
Our approach also provides a natural framework for studying models of assembly bias, 
since we can use the exact clustering properties of simulated halos as a function of 
any arbitrary halo properties in the catalog. With direct mock population, 
systematic uncertainty in the model is limited to 
the sample variance of the simulated box, 
errors related to insufficient numerical resolution, 
and numerical inaccuracies of halo-finding (e.g., over-merging).

@@

The most important detail of this analysis is the priors on the parameters. In all analyses 
discussed in this paper, we adopt priors that are uniform distributions over the intervals 
specified in Table~\ref{table:priors}. In the case of the assembly bias parameters 
$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors have strict  
boundaries. Mathematically, these parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
Physical considerations require parameter $\sigma_{\log M} > 0$. All other 
priors have a negligible influence on the posterior aside from $\log M_0$. 
We find that $\log M_0$ is often very poorly constrained by clustering data and 
priors on $\log M_0$ can have a non-negligible influence on inferred parameters.
